Monte Carlo and bootstrap for ALL parameters with tables

### 2024-08-26 All3_tables.Rmd
Changed rounds

```{r}
# True values
real_val <- c(nrow(trees), nrow(trees[(pi*trees$d130 < 70.5),]), nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), nrow(trees[(pi*trees$d130 > 117.5),]), 
  sum(trees$v), sum(trees[(pi*trees$d130 < 70.5),]$v), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), sum(trees[(pi*trees$d130 > 117.5),]$v), 
  round(sum(trees$v)/nrow(trees), digits = 2), round(sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), digits = 2), round(sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), digits = 2), round(sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),]), digits = 2)
  )

cat("True integrals are the following:\n\nNumber of trees:", real_val[1], "\nTotal volume:", real_val[5], 
    "\nWhich leads to the following ratio \"Total volume / Number of trees\":", real_val[9],
    "\n\nNumber of small trees:", real_val[2], "\nVolume of small trees:", real_val[6], 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val[10],
    "\n\nNumber of medium trees:", real_val[3], "\nVolume of medium trees:", real_val[7], 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val[11],
    "\n\nNumber of big trees:", real_val[4], "\nVolume of big trees:", real_val[8], 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val[12]
    )
```

```{r}
real_df <- data.frame(c("All trees", "Small trees", "Medium trees", "Big trees"), matrix(real_val, nrow = 4))
colnames(real_df) <- c("", "Number", "Volume", "Ratio Volume/Number")
```

>>>>

```{r}
# True values
real_val <- c(nrow(trees), nrow(trees[(pi*trees$d130 < 70.5),]), nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), nrow(trees[(pi*trees$d130 > 117.5),]), 
  sum(trees$v), sum(trees[(pi*trees$d130 < 70.5),]$v), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), sum(trees[(pi*trees$d130 > 117.5),]$v), 
  sum(trees$v)/nrow(trees), sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),])
  )

real_val_read <- c(nrow(trees), nrow(trees[(pi*trees$d130 < 70.5),]), nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), nrow(trees[(pi*trees$d130 > 117.5),]), 
  sum(trees$v), sum(trees[(pi*trees$d130 < 70.5),]$v), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), sum(trees[(pi*trees$d130 > 117.5),]$v), 
  round(sum(trees$v)/nrow(trees), digits = 3), round(sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), digits = 3), round(sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), digits = 3), round(sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),]), digits = 3)
  )

cat("True integrals are the following:\n\nNumber of trees:", real_val_read[1], "\nTotal volume:", real_val_read[5], 
    "\nWhich leads to the following ratio \"Total volume / Number of trees\":", real_val_read[9],
    "\n\nNumber of small trees:", real_val_read[2], "\nVolume of small trees:", real_val_read[6], 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val_read[10],
    "\n\nNumber of medium trees:", real_val_read[3], "\nVolume of medium trees:", real_val_read[7], 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val_read[11],
    "\n\nNumber of big trees:", real_val_read[4], "\nVolume of big trees:", real_val_read[8], 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val_read[12]
    )
```

```{r}
real_df <- data.frame(c("All trees", "Small trees", "Medium trees", "Big trees"), matrix(real_val_read, nrow = 4))
colnames(real_df) <- c("", "Number", "Volume", "Ratio Volume/Number")
```

### 2024-08-26 All_tables.Rmd
Changed rounds

```{r}
# True values
real_val <- c(nrow(trees), nrow(trees[(pi*trees$d130 < 70.5),]), nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), nrow(trees[(pi*trees$d130 > 117.5),]), 
  sum(trees$v), sum(trees[(pi*trees$d130 < 70.5),]$v), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), sum(trees[(pi*trees$d130 > 117.5),]$v), 
  round(sum(trees$v)/nrow(trees), digits = 3), round(sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), digits = 3), round(sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), digits = 3), round(sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),]), digits = 3)
  )

cat("True integrals are the following:\n\nNumber of trees:", real_val[1], "\nTotal volume:", real_val[5], 
    "\nWhich leads to the following ratio \"Total volume / Number of trees\":", real_val[9],
    "\n\nNumber of small trees:", real_val[2], "\nVolume of small trees:", real_val[6], 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val[10],
    "\n\nNumber of medium trees:", real_val[3], "\nVolume of medium trees:", real_val[7], 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val[11],
    "\n\nNumber of big trees:", real_val[4], "\nVolume of big trees:", real_val[8], 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val[12]
    )
```

```{r}
real_df <- data.frame(c("All trees", "Small trees", "Medium trees", "Big trees"), matrix(real_val, nrow = 4))
colnames(real_df) <- c("", "Number", "Volume", "Ratio Volume/Number")
```

>>>>

```{r}
# True values
real_val <- c(nrow(trees), nrow(trees[(pi*trees$d130 < 70.5),]), nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), nrow(trees[(pi*trees$d130 > 117.5),]), 
  sum(trees$v), sum(trees[(pi*trees$d130 < 70.5),]$v), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), sum(trees[(pi*trees$d130 > 117.5),]$v), 
  sum(trees$v)/nrow(trees), sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),])
  )

real_val_read <- c(nrow(trees), nrow(trees[(pi*trees$d130 < 70.5),]), nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), nrow(trees[(pi*trees$d130 > 117.5),]), 
  sum(trees$v), sum(trees[(pi*trees$d130 < 70.5),]$v), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), sum(trees[(pi*trees$d130 > 117.5),]$v), 
  round(sum(trees$v)/nrow(trees), digits = 3), round(sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), digits = 3), round(sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), digits = 3), round(sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),]), digits = 3)
  )

cat("True integrals are the following:\n\nNumber of trees:", real_val_read[1], "\nTotal volume:", real_val_read[5], 
    "\nWhich leads to the following ratio \"Total volume / Number of trees\":", real_val_read[9],
    "\n\nNumber of small trees:", real_val_read[2], "\nVolume of small trees:", real_val_read[6], 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val_read[10],
    "\n\nNumber of medium trees:", real_val_read[3], "\nVolume of medium trees:", real_val_read[7], 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val_read[11],
    "\n\nNumber of big trees:", real_val_read[4], "\nVolume of big trees:", real_val_read[8], 
    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val_read[12]
    )
```

```{r}
real_df <- data.frame(c("All trees", "Small trees", "Medium trees", "Big trees"), matrix(real_val_read, nrow = 4))
colnames(real_df) <- c("", "Number", "Volume", "Ratio Volume/Number")
```
